Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-09 constantRate/ConstCompFuzzExt-reorg.tex
adding full proof of sampling construction, reorganized

We construct the first fuzzy extractors that work for a large class of distributions that have negative minimum usable entropy. Their security is computational.  In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.

Our first construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.

@@

The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.

@@

\begin{lemma}
\label{lem:info theory sec}
Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.  Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.  Then the following is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-fuzzy conductor that is $\epsilon \ell$ hard with error $\delta$:

@@

\section{Achieving Reusability \& $\Huse\le 0$}
\label{sec:sampling}
In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with $\Huse \le 0$.  In this section we show that the addition of computational techniques yields considerable extra power.  Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.  This is known to be impossible in the information-theoretic setting.  
%\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.  Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.  In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously, at the price of  decreasing the effective error tolerance.
%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).

The main idea is to sample a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscate the concatenation of these blocks.  Denote this concatenated value by $V_1$.  This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.  We first present the necessary definitions and the construction.% and then compare it to \consref{cons:first construction}.  % and the construction proceeds by either obfuscating $V_i$ or a random point as before. 
For security each value $V_i$ needs to be unguessable.  
This will hold as long as enough blocks contribute some entropy:

\begin{definition}
\label{def:partial source}
A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
\end{definition}
\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.  The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.

@@

Before we show \thref{thm:sampling} we present a simplified construction of \consref{cons:sampling}.  This construction essentially ignores the sampling step and asks when obfuscation provides security of the obfuscated values $V_1,..., \ell$.  Our security argument for \consref{cons:sampling} will reduce to this simplified construction.  After presenting this simplified construction we will return to showing \thref{thm:sampling}.

\subsection{Simplifying \consref{cons:sampling}}
In this section, we present a simplified version of \consref{cons:sampling}. The goal of this construction is to understand the type of sources that \consref{cons:sampling} supports.  Furthermore, this simplified construction has some advantages over \consref{cons:sampling}.\footnote{For the sake of clarity we defer discussion of \consref{cons:first construction} until \apref{sec:construction}.  In this section we focus on understand what information is leaked by point obfuscations and digital lockers.}
%Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

\begin{construction}
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $V = V_1,..., V_\ell$ be a distribution over $\mathcal{Z}^\ell$.  Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.  Let  $C\subset \zo^\ell$ be an error-correcting code.
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $v = v_1,..., v_\ell$
\item Sample $c\leftarrow C$.
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item If $c_j = 0$: $p_j = \mathcal{O}(I_{v_j})$.
\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
\end{enumerate}
\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(v', p)$
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item If $p_j(v_j') = 1$: set $c_j' = 0$.
\item Else: set $c_j' = 1$.
\end{enumerate}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

The input $v$ is hidden in two different ways.  In locations where $c_j=1$, the block $v_j$ is information-theoretically unknown.
In locations where $c_j=0$, it is hard to find $v_j$ given access to the point obfuscation.
There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $v_j \neq v_j'$.  However, if a bit $c_j'$ is $0$, this likely means that $v_j=v_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).  This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $V_j$.  By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function. Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols. This restriction on the distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_v (\cdot, \cdot)$ be an oracle that returns \[I_v(j, v_j')=
\begin{cases}
1 & v_j = v_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $V = V_1||...|V_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(V_j |View(S^{I_{V}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We show some examples of unguessable block distributions in \apref{sec:characterize}.  In particular, any source $V$ where for all $j$, $\Hoo(V_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).

Intuitively, for a block unguessable distribution, the oracle provided by the obfuscation is not useful.  Indeed, we can show that \consref{cons:first construction} is a computational fuzzy conductor~(\apref{sec:construction}).  It is this observation that allows us to show the security of our \emph{sample-then-obfuscate construction}.  We will show that the output of the sampling part of the algorithm produces a unguessable-block distribution.
% For security we argue that each of the $v_i$ values is unguessable.  For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.  Reusability comes essentially for free given a sufficiently composable obfuscation for digital lockers.  For the sake of clarity we state reusability as a separate theorem~(\thref{thm:reusability}).

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
We now return to showing \thref{thm:sampling}.  
In order to show security \consref{cons:sampling}, we
show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  
Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

In ~\clref{cl:all blocks entropy} we show that any distribution where each individual block has super-logarithmic min-entropy forms a unguessable block distribution.  This allows us to conclude:
\begin{corollary}
\label{cor:v are unguessable}
Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}. Take any $q=\poly(n)$.  For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
\end{corollary}

Thus, unless the choice of $\lambda$ is very unlucky,
the inputs $V_1,..., V_\ell$ to \consref{cons:sampling} form a block unguessable distribution.  This is enough to show the probability that adversary sees a output other than $\perp$ from one of the obfuscations is negligible and that the adversary only has information about the key in this case.  
\begin{lemma}[Proof in \apref{sec:sampling unguess}]
\label{lem:samp unguess}
Let all the variables be as in \thref{thm:sampling}.
For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.% \geq H_0(C)$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{lemma}
%\begin{proof}
%Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
%\end{proof}

@@

\begin{lemma}[Proof in \apref{sec:sampling errors}]
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[\forall i, v_i\neq v_i'] <1 - \ngl(n)$, where the probability is over the coins of $\gen$.  
\end{lemma}

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} essentially follows from the security of the VGB obfuscator with auxiliary input.  We consider a bounded $q = \poly(n)$ number of reuses.  For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator must still be able to simulate.  Thus, given sufficiently strong reusability we achieve the following stronger result:

@@

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.  However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.

%\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}

@@

%\section{Use of Fuzzy Extractors for Biometrics}
%Fuzzy extractors derive stable from noisy sources.  Biometrics represent an important noisy physical source.  Unlike physical unclonable functions, biometrics are fixed distributions.  Biometrics cannot be redesigned to  increase their entropy or reduce their error rates.  Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).  Unfortunately, most work measures system security using false accept rate vs. false reject rate.  This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.  False accept rate provides no bound on the information leaked by the helper data.  Indeed the helper data may completely reveal the original input.  In high security applications, measuring false accept rate vs. false reject rate is insufficient to argue system security.
%
%\label{sec:iris no key}
%As an example, we focus on the human iris.  The iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.  The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.  Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.  There has been considerable research since the work of Daugman~\cite{daugman2004}.  These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.  We use the Daugman's parameters for our calculations.
%
%The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).  For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.%\footnote{Daugman  improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.  The comparison between the two readings is then made using bits not excluded by either image.  It is not clear how to extend into the fuzzy extractor setting.  Even with the masking vector $\Huse$ is negative for irises.}
%We have the following calculation for $\Huse$:
%\begin{align*}
%\Huse &= \Hoo(W) - \log |B_t|\\
%&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx 707.
%\end{align*}
%Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
%Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
%
%\section{Minimal Conditions for Fuzzy Extractor Security}
%\label{sec:minimal conditions}
%
%A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.  This means a negligible portion of the source distribution $W$ lies within any Hamming ball.  We make this intuition formal here:
%
%\begin{definition}
%\label{def:fuzzy min-ent}
%A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
%\[
%\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
%\]
%\end{definition}
%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
%\begin{lemma}
%\label{lem:fuzz necessary}
%Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
%\end{lemma}
%\begin{proof}
%Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
%\begin{itemize}
%\item On input $r, p$.
%\item If $\rep(m, p) = r$, output $1$.
%\item Else output $0$.
%\end{itemize}
%First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
%\[
%\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
%\]
%\end{proof}
%\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  %The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
%If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).  Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse\le 0$.   This motivates our restriction to meaningful classes of source distributions with $\Huse\le 0$.
%%This means we inherently must talk about the security and errors together.
%
%In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.  There are two minimal types of distributions where $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).  The other is that there $t+\omega(\log n)$ blocks that contribute some entropy~(there is a continuum between these two types).  Definitions~\ref{def:block guessable} and~\ref{def:partial source} were developed for these types of sources respectively.  However, we do not achieve security when $\Hfuzz(W)= \omega(\log n)$ for either definition, this is an open problem.
%
%\section{Fuzzy Conductors}
%\lnote{I need to check this}
%\label{sec:conductors}
%Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).  Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.  They suggest these bounds may be avoided by outputting a fresh random variable.  This is known as a fuzzy conductor~\cite{KanukurthiR09}.
%\begin{definition}
%A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
%\begin{enumerate}
%\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
%\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep(w', SS) = X]\geq 1-\delta$~(over the coins of $\gen', \rep'$).  If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
%\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.  That is, $\exists Y$ with $\Hav(Y | SS ) \geq \tilde{m}$ such that $\Delta((X, SS), (Y, SS))\leq \epsilon$.
%\end{enumerate}
%\end{definition}
%
%\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.  This motivates our use of a computational fuzzy conductor in \defref{def:comp fuzzy cond}.
%We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
%\begin{itemize}
%\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
%%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
%\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
%\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
%\end{itemize}
%Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.

>>>>

We construct the first fuzzy extractors that work for a large class of distributions that have negative minimum usable entropy. We present both information-theoretic and computational constructions.In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.

Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a large alphabet.  In this construction each symbol must contribute fresh entropy.  We then use computational techniques to obtain two constructions with additional properties.

@@

Our third construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.

The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.

@@

\noindent
For \consref{cons:info theoretic} to be secure we need most blocks to contribute some entropy to the output.  We call this notion a partial block source.

\begin{definition}
\label{def:partial source}
A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
\end{definition}
\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.  The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).

\begin{lemma}
\label{lem:info theory sec}
Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.  Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).

@@

\section{Achieving Reusability \& $\Huse\le 0$}
\label{sec:sampling}
In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with $\Huse \le 0$.  In this section we show that computational techniques allow for additional desirable properties.  Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.  This is known to be impossible in the information-theoretic setting.  
%\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.  Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.  In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously, at the price of  decreasing the effective error tolerance.
%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).

The main idea is to sample a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscate the concatenation of these blocks.  Denote this concatenated value by $V_1$.  This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.  
Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.

@@

%Before we show \thref{thm:sampling} we present a simplified construction of \consref{cons:sampling}.  This construction essentially ignores the sampling step and asks when obfuscation provides security of the obfuscated values $V_1,..., \ell$.  Our security argument for \consref{cons:sampling} will reduce to this simplified construction.  After presenting this simplified construction we will return to showing \thref{thm:sampling}.

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
%We now return to showing \thref{thm:sampling}.  
In this section we briefly describe why \consref{cons:sampling} is secure.  A proof of security appears \apref{sec:analysis sampling}.  
In order to show security \consref{cons:sampling}, we
show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

Once all $V_i$ all simultaneously have good entropy, the adversary will never see anything but $\perp$ as an output from the obfuscations~(with overwhelming probability).  If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:samp unguess}
Let all the variables be as in \thref{thm:sampling}.
For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.% \geq H_0(C)$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{lemma}
%\begin{proof}
%Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
%\end{proof}

@@

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[\forall i, v_i\neq v_i'] <1 - \ngl(n)$, where the probability is over the coins of $\gen$.  
\end{lemma}

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.  We consider a bounded $q = \poly(n)$ number of reuses.  For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator must still be able to simulate.  Thus, given sufficiently strong reusability we achieve the following stronger result:

@@

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} supports partial block sources with $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.  However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.

\section{Allowing Correlated Symbols}
In the previous two sections, we presented constructions that supported $\Huse\le 0$ for restricted classes of distributions.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting $\Huse \le 0$ and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

\begin{construction}
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.  Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.  Let  $C\subset \zo^\ell$ be an error-correcting code.
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C$.
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
\end{enumerate}
\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item If $p_j(w_j') = 1$: set $c_j' = 0$.
\item Else: set $c_j' = 1$.
\end{enumerate}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.  However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).  This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.  By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function. Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols. This restriction on the distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1| ... |W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We show some examples of unguessable block distributions in \apref{sec:characterize}.  In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
The following theorem states the construction is both correct and secure.  %After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.  Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
\end{theorem}

@@
